Coexistence with varying environmental filtering intensity

### 2018-07-06 env_intensity.Rmd
:hammer: Adapt code to new framework with weights

# Functions --------------------------------------------------------------------
generate_cor_traits = function(number_patches, number_species, number_other = 9,
                               cor_coef = 0.7) {

    # Initial Trait
    x1 = seq(1, number_patches, length.out = number_species)

    cov_mat = matrix(c(1, cor_coef, 0, sqrt(1 - cor_coef^2)), nrow = 2)

    n_other = number_other

    res = lapply(seq(n_other), function(x) {

        # Independent trait
        x2 = runif(number_species, 1, number_patches)

        # Correlated trait in second row
        cov_mat %*% matrix(c(x1, x2), nrow = 2, byrow = TRUE)

    })

    res = do.call(rbind, lapply(res, function(x) x[2,]))
    res = rbind(x1, res)

    res = t(res)

    # Repaste first column
    cbind(res[,1],

          # Scale all the traits between min and max value of x1
          sapply(2:ncol(res), function(x) {
              val = res[,x]

              (val - min(val))/(max(val) - min(val)) * (diff(range(x1))) +
                  min(x1)
          }))
}

# Compute a data.frame of number of individuals in function of optimal trait
# for competition and growth
landscape_df = function(multiple_traits_scenario, trait_types_row) {

    growth_traits = names(trait_types_row[trait_types_row %in% c("R", "RA")])
    compet_traits = names(trait_types_row[trait_types_row %in% c("A", "RA")])

@@

## Single Trait Competition
trait_type = c(trait1 = "A")
single_trait_compet = multigen(traits = traits, trait_type = trait_type,
                               env = env, time = time, species = species,
                               patches = patches, composition = composition,
                               A = A, d = d, k = k, width = width)
single_trait_compet_final = ifelse(single_trait_compet$compo[,,time] < 2, 0, single_trait_compet$compo[,,time])

## Single Trait Growth
trait_type = c(trait1 = "R")
single_trait_growth = multigen(traits = traits, trait_type = trait_type,
                               env = env, time = time, species = species,
                               patches = patches, composition = composition,
                               A = A, d = d, k = k, width = width)
single_trait_growth_final = ifelse(single_trait_growth$compo[,,time] < 2, 0,
                                   single_trait_growth$compo[,,time])

## Both
trait_type = c(trait1 = "RA")
single_trait_both = multigen(traits = traits, trait_type = trait_type,
                             env = env, time = time, species = species,
                             patches = patches, composition = composition,
                             A = A, d = d, k = k, width = width)

single_trait_both_final = ifelse(single_trait_both$compo[,,time] < 2, 0,
                                 single_trait_both$compo[,,time])

@@

```{r}
compute_moments = function(simulation_routine, trait_df = traits) {
    # CWM computation
    ab_rel = (simulation_routine$compo[,,150] / rowSums(simulation_routine$compo[,,150]))
    cwm_df = ab_rel %*% trait_df
    # Values stored in moments_df
    moments_df = as.data.frame(cwm_df)
    colnames(moments_df) = "cwm"
    moments_df = tibble::rownames_to_column(moments_df, "patch")
    moments_df$env = seq(patches)
    # Add CWV
    cwv_df = (ab_rel %*% trait_df^2) - cwm_df^2
    cwv_df = as.data.frame(cwv_df)
    colnames(cwv_df) = "cwv"
    cwv_df = tibble::rownames_to_column(cwv_df, "patch")
    moments_df = dplyr::left_join(moments_df, cwv_df, by = "patch")

both_cw = compute_moments(single_trait_both, traits)
colnames(both_cw) = c("patch", "both_cwm", "env", "both_cwv")
growth_cw = compute_moments(single_trait_growth, traits)
colnames(growth_cw) = c("patch", "growth_cwm", "env", "growth_cwv")
compet_cw = compute_moments(single_trait_compet, traits)
colnames(compet_cw) = c("patch", "compet_cwm", "env", "compet_cwv")

@@

## Generate several traits with various scenarios

### Moderately correlated traits (4 traits, various scenarios)

@@

# Number of trait influencing growth or competition
trait_types = t(data.frame(R8_A2 = c(rep("R", round(0.8*n_traits)),
                                     rep("A", n_traits - round(0.8*n_traits))),
                           R5_A5 = c(rep("R", round(0.5*n_traits)),
                                     rep("A", n_traits - round(0.5*n_traits))),
                           R2_A8 = c(rep("R", round(0.2*n_traits)),
                                     rep("A", n_traits - round(0.2*n_traits)))))
colnames(trait_types) = colnames(traits)

# Simulations ------------------------------------------------------------------
multiple_traits <- apply(trait_types, 1,
                         function(x){
                             multigen(traits = traits,
                                      trait_type = x,
                                      env = env,
                                      time = time,
                                      species = species,
                                      patches = patches,
                                      composition = composition,
                                      A = A, d = d,
                                      k = k, width = width)
                         })
names(multiple_traits) <- rownames(trait_types)

@@

sp_rich_final <- tidyr::gather(sp_rich_final, "prop_type", "richness", dplyr::contains("prop"))

@@

#### FD patterns

@@

#### Compute Null Models

@@

#### Number of Individuals Landscape and CWM

@@

```{r}
all_landscape = lapply(names(multiple_traits), function(scenario) {
    landscape_df(multiple_traits[[scenario]], trait_types[scenario,])
})
names(all_landscape) = names(multiple_traits)

@@

### Moderately correlated traits (3 traits)

#### Simulation Routine

@@

# Number of trait influencing growth or competition
trait_types = c(trait1 = "R", trait2 = "RA", trait3 = "A")

@@

#### Individuals Landscape and CWM

>>>>

# Functions --------------------------------------------------------------------
compute_moments = function(simulation_routine, trait_df = traits) {
    # CWM computation
    ab_rel = (simulation_routine$compo[,,150] / rowSums(simulation_routine$compo[,,150]))
    cwm_df = ab_rel %*% trait_df
    # Values stored in moments_df
    moments_df = as.data.frame(cwm_df)
    colnames(moments_df) = "cwm"
    moments_df = tibble::rownames_to_column(moments_df, "patch")
    moments_df$env = seq(patches)
    # Add CWV
    cwv_df = (ab_rel %*% trait_df^2) - cwm_df^2
    cwv_df = as.data.frame(cwv_df)
    colnames(cwv_df) = "cwv"
    cwv_df = tibble::rownames_to_column(cwv_df, "patch")
    moments_df = dplyr::left_join(moments_df, cwv_df, by = "patch")

# Compute a data.frame of number of individuals in function of optimal trait
# for competition and growth
landscape_df = function(multiple_traits_scenario, trait_weights) {

    growth_traits = subset(trait_weights, growth_weight != 0)$trait
    compet_traits = subset(trait_weights, compet_weight != 0)$trait

@@

## Single Trait Competition
trait_type = data.frame(trait = "trait1",
                        growth_weight = 0,
                        compet_weight = 1)
single_trait_compet = multigen(traits = traits, trait_weights = trait_type,
                               env = env, time = time, species = species,
                               patches = patches, composition = composition,
                               A = A, d = d, k = k, width = width)
single_trait_compet_final = ifelse(single_trait_compet$compo[,,time] < 2, 0, single_trait_compet$compo[,,time])

## Single Trait Growth
trait_type = data.frame(trait = "trait1",
                        growth_weight = 1,
                        compet_weight = 0)
single_trait_growth = multigen(traits = traits, trait_weights = trait_type,
                               env = env, time = time, species = species,
                               patches = patches, composition = composition,
                               A = A, d = d, k = k, width = width)
single_trait_growth_final = ifelse(single_trait_growth$compo[,,time] < 2, 0,
                                   single_trait_growth$compo[,,time])

## Both
trait_type = data.frame(trait = "trait1",
                        growth_weight = 1,
                        compet_weight = 1)
single_trait_both = multigen(traits = traits, trait_weights = trait_type,
                             env = env, time = time, species = species,
                             patches = patches, composition = composition,
                             A = A, d = d, k = k, width = width)

single_trait_both_final = ifelse(single_trait_both$compo[,,time] < 2, 0,
                                 single_trait_both$compo[,,time])
```

@@

```{r}
both_cw = compute_moments(single_trait_both, traits)
colnames(both_cw) = c("patch", "both_cwm", "env", "both_cwv")
growth_cw = compute_moments(single_trait_growth, traits)
colnames(growth_cw) = c("patch", "growth_cwm", "env", "growth_cwv")
compet_cw = compute_moments(single_trait_compet, traits)
colnames(compet_cw) = c("patch", "compet_cwm", "env", "compet_cwv")

@@

# Multiple traits

## Moderately correlated traits (4 traits, single influence)

@@

# Generate traits --------------------------------------------------------------
set.seed(1)
traits <- generate_cor_traits(patches, species, n_traits - 1, cor_coef = 0.3)

# Number of trait influencing growth or competition
trait_types = list(
    R3_A1 = data.frame(trait = paste0("trait", 1:4),
                       growth_weight = c(rep(1/3, 3), 0),
                       compet_weight = c(rep(0, 3), 1)),
    R2_A2 = data.frame(trait = paste0("trait", 1:4),
                       growth_weight = c(rep(1/2, 2), rep(0, 2)),
                       compet_weight = c(rep(0, 2), rep(1/2, 2))),
    R1_A3 = data.frame(trait = paste0("trait", 1:4),
                       growth_weight = c(1, rep(0, 3)),
                       compet_weight = c(0, rep(1/3, 3)))
)

# Simulations ------------------------------------------------------------------
multiple_traits <- lapply(
    trait_types,
    function(x){
        multigen(traits = traits,
                 trait_weights = x,
                 env = env,
                 time = time,
                 species = species,
                 patches = patches,
                 composition = composition,
                 A = A, d = d,
                 k = k, width = width)
    })

@@

sp_rich_final <- tidyr::gather(sp_rich_final, "prop_type", "richness", dplyr::contains("R"))

@@

plot_grid(plot_prop_sp_rich, plot_prop_sp_rich_patch)
```

### FD patterns

@@

### Compute Null Models

@@

### Number of Individuals Landscape and CWM

@@

```{r}
all_landscape = lapply(names(multiple_traits), function(scenario) {
    landscape_df(multiple_traits[[scenario]], trait_types[[scenario]])
})
names(all_landscape) = names(multiple_traits)

@@

## Moderately correlated traits (3 traits, one both)

### Simulation Routine

@@

# Number of trait influencing growth or competition
trait_types = list(
    RA20 = data.frame(trait = paste0("trait", 1:3),
                       growth_weight = c(0.8, 0.2, 0),
                       compet_weight = c(0,   0.2, 0.8)),
    RA50 = data.frame(trait = paste0("trait", 1:3),
                       growth_weight = c(0.5, 0.5, 0),
                       compet_weight = c(0,   0.5, 0.5)),
    RA80 = data.frame(trait = paste0("trait", 1:3),
                       growth_weight = c(0.2, 0.8, 0),
                       compet_weight = c(0,   0.8, 0.2))
)

@@

### Individuals Landscape and CWM
